Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-19 journal/article.tex
Choosing the agile model well

\subsubsection{Agile is found to be hard}

@@

@@

The choice of agile practices did affect the success of the transformation.
Also how the practices were choosen affected.

>>>>

\subsubsection{Agile is difficult to implement}

@@

* Some success factors are just calculated decisions that were made because
  the organization saw them as the best way to proceed. The question whether
  the decision really were critical for success is not proven.

@@

The choice of agile practices did affect the success of the transformation, and
also how the practices were choosen affected.

% Mapping agile to the old model

Mapping the agile model to match the old model was seen as necessary in a few
cases. Although a general mapping to the old model may not be good [P44, P46],
some cases needed to preserve high level management practices [P14, P29, P48].
By allowing management to remain unchanged it was possible to introduced agile
stepwise on team level, and helped in getting management buy-in for the process
[P14, P29, P48].
In one case Scrum was considered as a wrapper for existing practices, and could
therefore be easily fit in the organization [P44]. The agile methodology was
considered complementing the existing culture, which eased management buy-in for
the new method [P44].
% Similarities and differences of agile were documented, and Scrum terminology was
% explained in terms of the old model. Mapping of management information was done
% so that for instance the information earlier found in Engineering Gantt charts
% was found in the Sprint Backlog. [P29]

% Conformity in the agile model

Some studies reported that conformity was considered in implementing the new
model. A consistence common vocabulary was seen to benefit the organization and
support the change [P8, P16, P43]. Other benefits in using a single model were
possibility to compare work between teams, it was easier for people to relocate,
and progress was predictable for stakeholders [P43]. Consistency and common
understanding was created in discipline meetings and public events, or by peer
coaching [P11, P12, P32].
